Historical advances in medicine that did not need (or want) a randomized clinical

### 2020-01-25 paper/paper.Rmd
Finished section on Framingham

The Framingham study provided insights beyond cardiovascular disease. A 1964 study (@framingham-smoking) provided additional support to the link between smoking

>>>>

An early finding of the Framingham study, after the four year follow-up visit (@framingham-hypertension) established hypertension, obesity, and hypercholesteremia as risk factors for arteriosclerotic heart disease (a composite measure of myocardial infarction, angina pectoris, coronary occlusion, or myocardial fibrosis). In 1964, researchers used the Framingham cohort combined with a second cohort in Albany, New York  to establish a link between smoking and cardiovascular disease (@framingham-smoking) and contributed vital information to the 1964 surgeon general's report. Further work elaborated on the greater importance of the systolic measurement of blood pressure on the risk of heart disease (@framingham-systolic).

The number of findings from the Framingham study goes on and on, but more important than the number of studies is the way that this study changed clinical practice. The Framingham study changed the medical community's attitudes from the belief that heart disease as something to be treated to the belief that heart disease was something that could be prevented (@framingham-epidemiology).

#### Aspirin and Reye's syndrome

Reye's syndrome is rare disorder seen mostly in children. It can produce serious intracrainal swelling that can lead to serious neurological damage and possibly death.
